Hydras \& Co.

### 2023-11-29 doc/chapter-primrec.tex
Complete a remark in Chapter 11 (Alectryon output)

\begin{todo}
Fix the display the local definition of \texttt{x} in the following proof.
\end{todo}

>>>>

\begin{todo}
  Fix the display of the local definition of \texttt{x} in the following proof: \emph{Alectryon} prints a \emph{declaration} \texttt{x: nat}, but forgets to print the definition \texttt{x := Nat.max 2 m},  which is  important to complete the proof.
\end{todo}
